Another paper with lots of text and fancy pictures

### 2023-09-25 paper.tex
Replot F_{sss} comparison

To test $F_{sss}$ function we use a recently developed approach which computes
that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
with help of automatic differentiation \cite{postnicov20232}. We choose $f$
\begin{equation}
  f(x, y, z) = \sqrt{x^2 + y^2 + z^2}
\end{equation}
so inequation $f(x, y, z) \le T$ gives us a ball.

The test was performed by evaluating the inequation with the parameter $T = 0.2$
in a cube $[0, 1]^3$ and comparing $F_{sss}$ calculated with our algorithm with
precise values. The result of comparison is on
\cref{fig:sss-verification}. Maximal relative error for this case is about  15\%
when $F_{sss}(r_1, r_2)$ is calculated for $r_1$ and $r_2$ being not too close
to zero.
\begin{figure*}[tp]
  \centering
  \subfigure[Computation with our algorithm]{
    \includegraphics[width=0.45\linewidth]{images/ball-sss.png}
    \label{fig:balls-sss-comp}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/ball-sss-error.png}
    \label{fig:ball-sss-error}}
  \caption[]{Comparison of $F_{sss}$ function for a ball with the radius $0.2$
    with precise values.}
  \label{fig:sss-verification}
\end{figure*}

>>>>

To test $F_{sss}$ function we use a recently developed approach which computes
that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
with help of automatic differentiation \cite{postnicov20232}. We choose $f$
\begin{equation}
  f(x, y, z) = [(2x)^{\frac{3}{2}} + y^{\frac{3}{2}} + z^{\frac{3}{2}}]^{\frac{2}{3}}
\end{equation}
so inequation $f(x, y, z) \le T$ gives us an ellipse-like object
(\cref{fig:sss-ellipse}).

The test was performed by evaluating the inequation with the parameter $T = 0.4$
in a cube $[-1, 1]^3$ and comparing $F_{sss}$ calculated by our algorithm with
precise values. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-ellipse-error}. Maximal relative error in the area bound by
inequations $x > 0.1$, $y > 0.1$ and $f(x, y) < 0.78$ is about 10\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The ellipse-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.45\linewidth]{images/ellipse.png}
    \label{fig:sss-ellipse}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/ellipse-sss-diff.png}
    \label{fig:sss-ellipse-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise]{
    \includegraphics[width=0.45\linewidth]{images/ellipse-sss.png}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.45\linewidth]{images/ellipse-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}
